---
title       : Iris Prediction App
subtitle    : Predict the type of Iris
author      : qqaawkamai
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What does the app do?

- Iris is a genus of flowering plants.
- Iris means rainbow in Greek.
- Pretty much the coolest looking flowers out there.
- 3 species of Iris that are predicted in this model are:
    - Iris setosa
    - Iris versicolor
    - Iris virgincia
- Model takes the Petal and Sepal dimensions (length and width) and accurately
predicts the species of Iris.

--- .class #id 

## The Data

The Edgar Anderson Iris dataset (provided in R) is used in the app.

```{r}
data(iris)
summary(iris)
```

--- .class #id

## The Model

Random Forest library is used to build a fairly accurate prediction model based on Sepal and Petal dimensions.

```{r, results='hide'}
library(randomForest)
```

```{r}
modFit <- randomForest(Species ~., data=iris)
modFit$err.rate[500,1]
modFit$confusion
```

--- .class #id

## The Model - continued

- The model has a very low error rate (~5%).
- From the confusion matrix, we see that very few are misclassified.
- Thus, putting in the Petal and Sepal dimensions in the app, will accurately
predict the species of iris.
- [Link to Shiny App](https://qqaawkamai.shinyapps.io/iris/)
